\documentclass[11pt,english]{article}
\usepackage[letterpaper,bindingoffset=0.2in,%
            left=0.3in,right=0.3in,top=0.4in,bottom=0.4in,%
            footskip=.25in]{geometry}
%\documentclass[letterpaper,11pt]{article}
%\pagestyle{empty}
\usepackage[svgnames]{xcolor}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{hyperref}
\usepackage{tocloft}
\usepackage{enumitem}
\setlist{nosep}
\setlength{\parindent}{0in}

        %\setlength{\itemsep}{0pt}


\begin{document}
\textbf{\Large Jack Doan}
\hfill
214-436-6105\\
2800 Waterview Pkwy, Apt 6231
\hfill
hello@jackdoan.com \\
Richardson, TX 75080
\hfill
jackdoan.com \\
\textcolor[RGB]{220,220,220}{\rule{\linewidth}{0.2pt}}

\vspace{0.5em}
\textbf{Summary:} Computer Engineer with leadership experience and academic training at the University of Texas at Dallas. Proven skills in circuit design, research, and system integration, with a strong background in both embedded systems and electric motor control.

\vspace{0.75em}
\textbf{Education:} The University of Texas at Dallas, B.S. Computer Engineering, May 2018
\hfill
GPA: 3.1/4.0 \\
Coursework: Computer Architecture, Real Time Operating Systems, Signals \& Systems

\vspace{0.75em}
\textbf{Engineering Projects and Experience:}\\
Student Researcher at the Locomotor Control Systems Laboratory
\hfill
April 2015 - Current
\begin{itemize}
    \item Control Strategy Implementation:
    \begin{itemize}
        \item Worked with PhD candidates to get their control strategies off of the whiteboard and into reality
        \item Transformed scientific literature into precise, testable software requirements
        \item Used Agile methodologies to develop software quickly, while ensuring the user’s needs were met
        \item Documented code to allow non-programmers to understand and tweak it
        \item Successfully tripled system performance by overhauling legacy code to meet modern standards
    \end{itemize}
    \item Comet Exoskeleton:
    \begin{itemize}
        \item The Comet Exoskeleton is a powered lower-leg orthotic device that helps its wearer walk
        \item Designed to facilitate rehabilitation of stroke patients who need to learn to walk again
        \item Capable of fully tracking the user’s gait cycle and applying the up to 40\% body weight support
        \item Implemented control laws, wrote device drivers and designed printed circuit boards
        \item Operated the device \& monitored sensor data for safety during human subject experiments
    \end{itemize}
\end{itemize}
\vspace{0.5em}
Electrical Team Leader for UTD Combat Robotics
\hfill
October 2014 - May 2017
\begin{itemize}
    \item Designed, built and competed with UTD’s flagship combat robot: The Blender
    \item Built with a titanium shell, 9000 Watts of electric motors, and four steel teeth spinning at over 100 mph
    \item Designed custom motor controllers, which save the team an average of \$200 per round of combat
    \item Led the team to a smashing success in 2015, with a 3rd place finish at the international RoboGames
\end{itemize}
\vspace{0.5em}

\textbf{Publications:}
\begin{itemize}
    \item H. Zhu, \textbf{J. Doan}, C. Stence, G. Lv, T. Elery, R. Gregg, `Design and validation of a torque dense, highly backdrivable powered knee-ankle orthosis' \textit{IEEE Int. Conf. Robotics and Automation}, 2017.
\item T. Elery, S. Rezazadeh, C. Nesler, \textbf{J. Doan}, H. Zhu, R. Gregg, `Design and benchtop validation of a powered knee-ankle prosthesis with high-torque, low-impedance actuators' \textit{Submitted: IEEE Int. Conf. Robotics and Automation}, 2018.\\
\end{itemize}

\begin{tabular}{@{}l l l l l l}
    \textbf{Technical} & C/C++ & LabVIEW & DSP  & Verilog & Embedded Systems \\
    \textbf{Skills}    & KiCAD & Linux   & Java & Python  & Motor Control \\
                       & Altium & Git & RTOS & Battery Management & Communication Protocols \\
                       & AVR & ARM & MSP430 & C2000 & Use of Test Equipment\\
\end{tabular}

\vspace{0.5em}
\textbf{Availability:} Full time: May 2018. US Citizen. Willing to relocate.
\end{document}
